Query Optimization for Dynamic Imputation

### 2017-07-03 paper/algorithm.tex
some changes for camera-ready, see slack post
camera ready fix: explain L_{p(q)} a bit earlier

\subsubsection{Imputation quality} 
\label{sec:quality}
Each imputation method has an associated cost function $P$, which is a measure of the quality of its output.
\ProjectName{} estimates the aggregate quality of the imputations in a plan $q$ using the heuristic measure $\textsc{Penalty}_{P}(q)$, computed as follows.

@@

\subsubsection{Mean}\label{subsubsec:mean}

>>>>

\subsubsection{Imputation quality} 
\label{sec:quality}
Each imputation method has an associated cost function $P$, which is a measure of the quality of its output.
\ProjectName{} estimates the aggregate quality of the imputations in a plan $q$ using the heuristic measure $\textsc{Penalty}_{P}(q)$. \cameraready{Underlying
this is a helper function $\textsc{L}_{P(q)}$, which
is a recursive accumulator of penalties along imputation nodes instantiated
with an impute-specific penalty operator. This accumulator is computed
as follows.}

@@

\subsubsection{\cameraready{Non-Blocking Approximate Mean}}\label{subsubsec:mean}
